\mytitle

### 2023-05-25 generated/make-help.tex
Revisions for Computer Journal
Fixing makefile and deleteing obsolete files on Git

% Edit makefile to change the selected make command choices, as follows:
% 1 - make all
% 2 - make archive
% 3 - make check-same
% 4 - make check-update
% 5 - make check-versions
% 6 - make data
% 7 - make expand
% 8 - make help
% 9 - make help-brief
% 10 - make mathematica
% 11 - make mathematica-open
% 12 - make one-file
% 13 - make pdf
% 14 - make push
% 15 - make readme
% 16 - make really-tidyup
% 17 - make tidyup
% 18 - make zip
% 19 - make zip-data

@@

\texttt{make help}&
      Explain how to use \texttt{make}, and list all available options for using \texttt{make}.\\
   \multicolumn{1}{l@{\vdots}}{}&\\

\texttt{make tidyup}&
      Tidyup before doing a Git commit. Remove all easily generated files, and the large Git repositories needed for the pilot survey. Do not remove the main PDFs, or the \LaTeX\ data include files. Do not remove the .aux files, as \LaTeX\ runs much more smoothly with them.\\
\end{tabular}}

>>>>

% Edit makefile to change the selected make command choices, as follows:
% 1 - make all
% 2 - make archive
% 3 - make check-same
% 4 - make check-update
% 5 - make check-versions
% 6 - make data
% 7 - make expand
% 8 - make git-prep
% 9 - make help
% 10 - make help-brief
% 11 - make mathematica
% 12 - make mathematica-open
% 13 - make one-file
% 14 - make pdf
% 15 - make push
% 16 - make readme
% 17 - make really-tidyup
% 18 - make tidyup
% 19 - make zip
% 20 - make zip-data

@@

\texttt{make git-prep}&
      What's on Git that we've lost, or stuff we have got locally but probably don't want on Git, so you can delete it or move it out the way or whatever.\\
   \multicolumn{1}{l@{\vdots}}{}&\\

\texttt{make really-tidyup}&
      More thorough than \texttt{make tidyup} --- remove \emph{all} files that can be recreated. (This will mean next time you run \LaTeX\ you will have to ignore errors as the .aux files are re-created.)\\
\end{tabular}}

### 2023-05-25 generated/over-fitting-code-section.tex
Fixing makefile and deleteing obsolete files on Git

Reference \cite{may-simple} shows that even trivial code (in the case cited, implementing simple difference equations) with very few parameters can have very complex results, and reference \cite{dyson} is a historically significant example how pointing out the problem of over-fitting has improved science.

>>>>

Reference \cite{may-simple} shows that even trivial code (in the case cited, implementing simple difference equations) with very few parameters can have very complex results, and reference \cite{dyson} is a historically significant paper pointing out how the problems of over-fitting has improved science.

### 2023-05-25 paper-seb-main.tex
Fixing makefile and deleteing obsolete files on Git

Systems like \LaTeX\ (which was used for the current paper) can combine advanced typesetting with computable paper calculations. Here, as a simple example, we calculate that
$10!$ is equal to \factorial{10} just by writing the \LaTeX\ code \verb|\factorial{10}| \emph{in\/} this paper to calculate arbitrary factorials and group the result into conventional blocks of three digits by inserting small spaces. Note that although \texttt{factorial} is not a standard \LaTeX\ function, it was readily defined by code also \emph{in\/} the present paper, so it can be easily modified by the author for other purposes as required.

@@

where the \the\countAuthors\ is the calculated number, save that line of text to a file, which is then import it into the paper where it is typeset in the normal way. Then, when and wherever the authors write the name \texttt{\textbackslash numberOfAuthors} in their paper's text, the typeset paper says \the\countAuthors, or whatever the actual value is at the time. Some easy \LaTeX\ coding can then present the numbers in the publisher's preferred style, such as \numbertoname 0, \numbertoname 1, \ldots\ \numbertoname 9, \numbertoname{10}, \numbertoname{11}, \ldots, \digitBlock{1000},  \digitBlock{1001}, etc, as done (more realistically) in this paper's footnote~\numbernamesexamplefootnote.

@@

\bibnewcolumn = 122 % bibentry number of last entry on (final) left hand column
% Hint: first set it to a very large number, so the final column is as unbalanced as it gets
% then, if it's worth fixing the final page, lower the number to some citation on the 
% lower part of the left hand column; this citation will then become the last in that
% column. Hopefully the righthand column will be of equal length!
% PS Don't forget to check there is nothing on the following page!

>>>>

Systems like \LaTeX\ (which was used for the current paper) can combine advanced typesetting with computable paper calculations. Here, as a simple example, we calculate that
$10!$ is equal to \factorial{10} just by writing the \LaTeX\ code \verb|\factorial{10}| \emph{in\/} this paper, which can calculate arbitrary factorials and group the result into conventional blocks of three digits by inserting small spaces. Note that although \texttt{factorial} is not a standard \LaTeX\ function, it was readily defined by code also \emph{in\/} the present paper, so it can be easily modified by the author for other purposes as required.

@@

where the \the\countAuthors\ is the calculated number, save that line of text to a file, which is then import it into the paper where it is typeset in the normal way. Then, when and wherever the authors write the name \texttt{\textbackslash numberOfAuthors} in their paper's text, the typeset paper says \the\countAuthors, or whatever the actual value is at the time. Some easy \LaTeX\ coding can then present the numbers in the publisher's preferred style, such as \numbertoname 0, \numbertoname 1, \ldots\ \numbertoname 9, \numbertoname{10}, \numbertoname{11}, \ldots, \digitBlock{1000},  \digitBlock{1001}, etc, as done more realistically elsewhere in this paper (for instance, see footnote~\numbernamesexamplefootnote).

@@

\bibnewcolumn = 123 % bibentry number of last entry on (final) left hand column
% Hint: first set it to a very large number, so the final column is as unbalanced as it gets
% then, if it's worth fixing the final page, lower the number to some citation on the 
% lower part of the left hand column; this citation will then become the last in that
% column. Hopefully the righthand column will be of equal length!
% PS Don't forget to check there is nothing on the following page!
